Scikit-learn: API design for machine learning

### 2013-06-19 paper.tex
requirements: shorten sentence
condense "Extending" section

To ease code reuse, simplify implementation and skip the introduction of
superfluous classes, the principle of \textit{duck typing} is exploited all
throughout the codebase. This technique allows both for extensibility and
flexibility: as long as an estimator follows our API and conventions (as
outlined in Section~\ref{sec:core-api}), then it should be as reusable as any
built-in estimator (e.g., it can plugged within pipelines or grid search
estimators). That is, estimators are specified only by their interface, and not
by inheritance. In particular, this means that external developers can define
their own estimators without being forced to inherit from any internal class of
\sklearn, and rest assured that they can be used as first-class estimators.

In other places of the library, in particular in the feature extraction and
vectorization code for text documents, the toolkit is also designed to be
extensible. Here, estimators provide hooks for user-defined code: objects or
functions that provide a specific API can be given as arguments at vectorizer
construction time. The library then calls into this code to obtain the desired
behavior. Again, such external user code can be kept agnostic of the \sklearn
class hierarchy and operates, for example, on standard Python objects such as
strings instead.

@@

To facilitate the adoption and the distribution of \sklearn,
the set of external dependencies is kept to a bare minimum:
only Python, NumPy and SciPy are required for a functioning installation.
Binary distributions of these are available for the major platforms.
Visualisation functionality depends on Matplotlib \citep{hunter2007matplotlib}
and/or Graphviz \citep{gansner2000},
but neither is required to do machine learning.
When feasible, external libraries are integrated into the codebase.
In particular, the codebase includes modified versions
of \textsf{LIBSVM} and \textsf{LIBLINEAR}
\citep{chang2011libsvm,fan2008}, both written in C{}\verb!++! and wrapped using
Cython modules.

>>>>

To ease code reuse, simplify implementation and skip the introduction of
superfluous classes, the principle of \textit{duck typing} is exploited
throughout the codebase. This technique allows both for extensibility and
flexibility: as long as an estimator follows the API and conventions
outlined in Section~\ref{sec:core-api}, then it can be used in lieu of a
built-in estimator (e.g., it can plugged into pipelines or grid search).
That is, estimators are defined only by interface, not by inheritance,
and external developers are not forced to inherit from any \sklearn class.

In other places of the library, in particular in the feature extraction and
vectorization code for text documents, the toolkit is also designed to be
extensible. Here, estimators provide hooks for user-defined code: objects or
functions that provide a specific API can be given as arguments at vectorizer
construction time. The library then calls into this code to obtain the desired
behavior. Again, such external user code can be kept agnostic of the \sklearn
class hierarchy.
Communication proceeds by passing object of standard Python/NumPy types.

@@

To facilitate the adoption and the distribution of \sklearn,
the set of external dependencies is kept to a bare minimum:
only Python, NumPy and SciPy are required for a functioning installation.
Binary distributions of these are available for the major platforms.
Visualisation functionality depends on Matplotlib \citep{hunter2007matplotlib}
and/or Graphviz \citep{gansner2000},
but neither is required to do machine learning.
When feasible, external libraries are integrated into the codebase.
In particular, modified versions of \textsf{LIBSVM} and \textsf{LIBLINEAR}
\citep{chang2011libsvm,fan2008}, both written in C{}\verb!++! and wrapped using
Cython modules.
